%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Projects}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventrytwo
{Automatic Speech Recognition System {\normalfont{\bodyfont(C/C++, CUDA, Kaldi)}}} % Organization
{Mar. 2015 -  Jul. 2015} % Location
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Implemented a deep neural network and N-best Viterbi algorithm to get n-best phone sequences and used Weighted Finite State Machine to decode them into word sequences}
\item {Built a Recurrent Neural Network Language Model to rescore all possible word sequences to get the best one}
\end{cvitems}
}

\cventrytwo
{Special Effect Film {\normalfont{\bodyfont(Blender3D)}}} % Organization
{Mar. 2015 -  Jul. 2015} % Location
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Created 3D models by Blender3D and used match moving to insert them into live-action footage}
\end{cvitems}
}

\cventrytwo
{Query-by-Singing/Humming System Based on Dynamic Programming {\normalfont{\bodyfont(Matlab)}}} % Organization
{Sep. 2014 -  Jan. 2015} % Location
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Designed a system based on pitch tracking and dynamic time warping that allows users to find a song from music databases by singing or humming a short snippet of the song, which \textbf{achieves accuracy \textasciitilde90\%}}
\end{cvitems}
}

\cventrytwo
{Functionally Reduced And-Inverter Graph {\normalfont{\bodyfont(C++)}}} % Organization
{Sep. 2013 -  Jan. 2014} % Location
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Applied optimization techniques to reduce the digital circuit size and simulation time
by finding functionally equivalent candidate (FEC) pairs in C++}
\end{cvitems}
}

\end{cventries}